Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-04 Ben_Manuscripts/structure_paper/Draft.tex
Comments on section 3.2.2

  % BJC8: Is it necessary to focus in on the parallel displaced system for this section? At this
  % point in the story, I haven't shown that it gives rise to R-double. I think the simple systems
  % are conceptually easier to grasp with sandwiched columns. Sliding parallel displaced columns
  % is harder to imagine, and probably not really how the columns are stacked. The parallel displacement
  % is probably less exagerated. 
  % BJC8: that said, if we go with just focusing on parallel displaced, then I can move the R-double section
  % up before this one.
  R-$\pi$ is more intense relative to the experimental system. In this section, we use the parallel displaced
  configuration in the ordered basin as an example, however all systems display this behavior.
  %since it is the most experimentally consistent system we've studied so far. 
  The intensity of R-$\pi$ in the ordered parallel displaced system is approximately 3 times
  larger than experiment (Table~\ref{table:relative_inensities_300K}).

  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). Each FWHM
  is larger than experiment. Note that the experimental data is best fit with a Lorentzian 
  function while the simulated patterns are best fit using a Gaussian function. The experimental
  pattern also has additional sources of broadening which, if deconvoluted, would increase the discrepancy with
  simulation.
  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \caption{(a) Experimentally, R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
  fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. (c) In our simulations, the FWHM of R-$\pi$ in
  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
  in the fit.}\label{fig:rpi_exp_comparison}
  \end{figure}

  Here we present our understanding of what factors influence the intensity of R-$\pi$ 
  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
  potential contributions which can be modified in our model by adjusting the simulation
  conditions, forcefield or initial configuration. We assessed each using a simplified 
  model. Our simplified model represents each monomer head group as a single point and
  places them in either a parallel displaced or sandwiched configuration. We apply 
  various transformations in order to study its simulated diffraction pattern.

  As a baseline, we created a simplified model using the same amount of disorder present
  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
  atoms and quenched disorder which is created by rapid structural rearrangement during
  early equilibration and is locked into place for the remainder of the simulation time. The
  latter has important implications for the reproducibility of this work since velocity
  randomization at the beginning of equilibration will result in different quenched 
  configurations. We measured thermal disorder by measuring the standard deviation in
  the distribution of head group center of mass positions from their average positions.
  We measured quenched disorder by calculating the standard deviation of the distribution 
  of head group center of masses from their ideal positions. In the z-direction, we measured
  the deviation of the head group center of masses from an equally spaced column of head groups.
  In the xy plane, we calculated the deviation in radial position from the pore center and 
  the angular deviation from equally spaced points surrounding the pore center. The values
  measured for each system are given in Table~\ref{table:quenched_disorder}. We built a simple
  system consisting of 1000 independent configurations using these parameters. We also made
  the simple system 4 times taller in order to get better resolution in the $q_z$ direction. 
  Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ generated by
  simulating the structure factor of the trajectory.

  %BJC8: Need to add thermal noise to this table
  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccc}
  \toprule
  System                        & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
  \midrule
  Ordered Sandwiched            &        1.48        &     0.43              &     2.30           \\
  Ordered Parallel Displaced    &        1.45        &     0.43              &     2.28           \\ 
  Disordered Sandwiched         &        1.58        &     0.43              &     2.93           \\
  Disordered Parallel Displaced &        1.65        &     0.43              &     2.63           \\
  \bottomrule
  \end{tabular}
  \caption{We measured the deviation of the positions of the center of mass of head groups from
  idealized positions so that we could incorporate the same disorder into our model system.}
  \label{table:quenched_disorder} 
  \end{table}

  %BJC8: Create parallel displaced configuration: create sandwiched system. Apply uniform rotation to every other layer
  %BJC8: I'd like to make the point somewhere that the real configuration is somewhere between sandwiched and the
  % parallel displaced configuration shown here.
%  There is no major difference between R-$\pi$ of a parallel displaced system and a 
%  sandwiched system.
%  \begin{itemize}
%  	\item Intensity does not change
%  	\item 
%  \begin{itemize}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation.png}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation.png}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the z, 
  $\theta$ and r directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
  increases but the sharp peaks remain with the same ratio of intensity between the
  center and outer peaks. (c) Correlation between scatterers in the z-direction causes
  R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  \end{figure}

  Scatterers in each column are correlated with each other. In the simplified 
  system described above, we added uncorrelated Gaussian noise in the 
  z-direction which ignores any interaction head groups might have with each
  other. To remedy this, we randomly sampled a multivariate normal distribution
  with the same variance, v, implied by Table~\ref{table:quenched_disorder}. We 
  defined the distribution using a covariance matrix such that the covariance
  in position, z, between scatterers decays exponentially from v according to the
  equation $ve^{-z/L}$, where L is the correlation length. Experimentally, the
  correlation length can be estimated as the inverse of the FWHM of the $q_z$
  cross-section of R-$\pi$.  %BJC8: needs references 
  Accordingly, the correlation length of the experimental system is $\geq$ 9 
  $\AA$. The value may be larger since the peak is likely broadened for a variety
  of other reasons. %BJC8: the reasons I can provide more detail on above.  
  %BJC8: Can show correlation effect on intensity in supporting info

@@

  %BJC8: The next couple paragraphs is all old stuff that can likely be cut down a bit. But I think 
  % this is where I'd put this discussion.
  Monomers in the ordered basin stack closer together than those in the disordered basin
  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
  disordered basin in the sandwiched and parallel displaced configurations respectively. 
  The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
  cases. This behavior is not surprising since GAFF models atoms as point charges and does not 
  appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
  favorable for the monomers to stack closer together. Additionally, it is possible that the 
  tails prevent close stacking of monomer head groups and we do not achieve the timescales 
  necessary for them to rearrange into a necessarily more tightly packed configuration. Ordered
  basin systems are likely the best choice for transport studies.

@@

  When we allow monomer columns to move independently in the z-direction, the intensity
  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
  smooths out.
  \begin{itemize}
  	\item Allowing columns to move independently smooths out the $q_r$ cross-section. Any amount
  	of dependence results in sharp peaks.
  	\item R-$\pi$ intensity decreases by up to 10x
  	\item Can put R-$\pi$ intensity vs. column independence in supporting info.
  	\item Predict level of independence in simulation (what amount of displacement cause the 
  	R-$\pi$ profile to look like that shown in Figure 8d).
  	\item Figure: (a) x \% column displacement give Figure 8d (b) Independent columns give a smooth
  	curve
  \end{itemize}

  Increasing thermal noise in the x and y directions causes R-$\pi$ to sharpen in the 
  $q_r$ direction.
  \begin{itemize}
    \item $q_r$ cross-section still too broad
    \item Adding more thermal noise sharpens it
    \item Figure: Overlay thinner FWHM plot on top of wider FWHM 
  \end{itemize}

  We have nearly the right amount of disorder / noise in our system, but correlation 
  between columns really messes up R-$\pi$.

@@

  The system size does not significantly alter the intensity of R-$\pi$. We equilibrated a 
  sandwiched system with twice as many monomers per column so that the system size doubled in 
  the z-direction. The correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA, 
  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
  are nearly identical (See Figure~S-\ref{S-fig:z_correlation_overlay}).

>>>>

  % BJC8: Is it necessary to focus in on the parallel displaced system for this section? At this
  % point in the story, I haven't shown that it gives rise to R-double. I think the simple systems
  % are conceptually easier to grasp with sandwiched columns. Sliding parallel displaced columns
  % is harder to imagine, and probably not really how the columns are stacked. The parallel displacement
  % is probably less exagerated. 
  % BJC8: that said, if we go with just focusing on parallel displaced, then I can move the R-double section
  % up before this one.
  % MRS9: I think we should start with larger differences rather than smaller, and arguably the greater intensity of R-pi is 
  % a bigger difference.  So it's OK ti put R-double after -- (and it could be that sliding sandwiched columns could still give water h-bonding, since they have carboxyl groups that are on average closer together than sandwiched layered ones).
  R-$\pi$ is more intense relative to the experimental system. In this section, we use the parallel displaced
  configuration in the ordered basin as an example, however 
%MRS9: should be a little more clear why you mean by ``all systems''.  In some sense the problem is more that the best explanation might be unaligned columns, which is easier with sandwiched, which are 15 times as much.  So here it would make more sense to focus on both types of columns, so you can explain how unaligned (sliding) columns also have a mechanism for reduction.  Note that I don't think the columns have to be dynamically sliding (Which would be hard with all the tails entangled) but can be just off-register statically.
all systems display this behavior.
  %since it is the most experimentally consistent system we've studied so far. 
  The intensity of R-$\pi$ in the ordered parallel displaced system is approximately 3 times
  larger than experiment (Table~\ref{table:relative_inensities_300K}).

  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections of R-$\pi$ 
  are in moderate agreement with experiment (Figure~\ref{fig:rpi_exp_comparison}). Each FWHM
  is larger than experiment. 
  %MRS9: state how much larger they are than experiment in the sentence before - big difference beween 30% bigger and 300% bigger.
Note that the experimental data is best fit with a Lorentzian 
  function while the simulated patterns are best fit using a Gaussian function. The experimental
  pattern also has additional sources of broadening which, if deconvoluted, would increase the discrepancy with
  simulation.
  %MRS9: State explicitly in what way the discrepancy would increase, i.e. experimental FWHM are broadened by other source (doppler pressure, insttrument broadening) that do no affect the simulated spectra, the experimental spectra may be even narrower than spectra generated from simulations are.  
  %MRS9: one question, do any of the approximations used in the simulation actually lead to broadening that would not be in experiment (gaussian scatterers, etc.  Also, (semi-related) do Gaussian scatters lead to Gaussian peaks? Fourier transforms of Gaussians are Gaussians) 
  % BJC8: Can add more detail about different types of broadening - instrument / finite resolution broadening (for
  % experimental case), doppler (gaussian shaped) and pressure broadening (Lorentzian shaped)
  % See: https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-7
  %MRS 9: it is a little problematic to use two different types of fit, as the FWHM is a little different for each of then. Would lead to slight discrepancies from that.  FWHM is a natural scale parameter for Lorenzians, but not really for Gaussian.  
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \caption{
   %MRS9: suggest something like this to make crystal clear A and B are from the experiments.
  In experiments ((a) and (b)), 
%Experimentally,  (a) 
  (a), R-$\pi$ broadens in the $q_z$ direction with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when
  fit with a Lorentzian function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792 
  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. (c) In our simulations, the FWHM of R-$\pi$ in
  the $q_z$ direction is 0.194 $\pm$ 0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width
  of experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01 $\AA^{-1}$ when fit with
  a Gaussian function, about 20 \% larger than experiment. Note that the large spike in the center is not included
  in the fit.}\label{fig:rpi_exp_comparison}
  \end{figure}

%MRS9: Could be stronger thesis.  Suggest
We have identified a number of potential ways that simulations conditions, forcefield and initial configurations could affect the intensity of R-$\pi$ as well its FWHM in the $q_z$ and $q_r$ directions
%Here we present our understanding of what factors influence the intensity of R-$\pi$ 
%  as well its FWHM in the $q_z$ and $q_r$ directions. We have identified a number of 
%  potential contributions which can be modified in our model by adjusting the simulation
%  conditions, forcefield or initial configuration. 
We assessed each using a simplified 
  model. Our simplified model represents each monomer head group as a single point and
  places them in either a parallel displaced or sandwiched configuration. We apply 
  various transformations in order to study its simulated diffraction pattern. 
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.
  As a baseline, we created a simplified model using the same amount of disorder present
  in our atomistic simulations. There are two sources of disorder to consider: thermal motion of
  atoms and quenched disorder which is created by rapid structural rearrangement during
  early equilibration and is locked into place for the remainder of the simulation time. The
  latter has important implications for the reproducibility of this work since velocity
  randomization at the beginning of equilibration will result in different quenched 
  configurations. 
  %MRS9: could be that initial starting configurations would ALSO give rise to different quenched configurations.
We measured thermal disorder by measuring the standard deviation in
  the distribution of head group center of mass positions from their average positions.
  We measured quenched disorder by calculating the standard deviation of the distribution 
  of head group center of masses from their 
%ideal positions. 
idealized average positions.
In the $z$-direction, we measured
  the deviation of the head group center of masses from an equally spaced column of head groups.
  In the $xy$ plane, we calculated the deviation in radial position from the pore center and 
  the angular deviation from equally spaced points surrounding the pore center. The values
  measured for each system are given in Table~\ref{table:quenched_disorder}. We built a simple
  system consisting of 1000 independent configurations using these parameters. We also made
  the simple system 4 times taller in order to get better resolution in the $q_z$ direction. 
  Figure~\ref{fig:sf_qy_nocorrelation} shows the $q_y$ cross-section of R-$\pi$ generated by
  simulating the structure factor of the trajectory.

  %BJC8: Need to add thermal noise to this table
  \begin{table}[h]
  \centering
  \begin{tabular}{c|ccc}
  \toprule
  System                        & $\sigma_z$ ($\AA$) & $\sigma_\theta$ (rad) & $\sigma_r$ ($\AA$) \\
  \midrule
  Ordered Sandwiched            &        1.48        &     0.43              &     2.30           \\
  Ordered Parallel Displaced    &        1.45        &     0.43              &     2.28           \\ 
  Disordered Sandwiched         &        1.58        &     0.43              &     2.93           \\
  Disordered Parallel Displaced &        1.65        &     0.43              &     2.63           \\
  \bottomrule
  \end{tabular}
  %MRS9: tweaked
  \caption{Deviation of the positions of the center of mass of head groups from
  idealized positions to use as simulated disorder into our model system.}
  \label{table:quenched_disorder} 
  \end{table}

  %BJC8: Create parallel displaced configuration: create sandwiched system. Apply uniform rotation to every other layer
  %BJC8: I'd like to make the point somewhere that the real configuration is somewhere between sandwiched and the
  % parallel displaced configuration shown here.
  %MRS9: better to say ``data is most consistent with the idea that the real configuration is somewhere between''
%  There is no major difference between R-$\pi$ of a parallel displaced system and a 
%  sandwiched system.
%  \begin{itemize}
%  	\item Intensity does not change
%  	\item 
%  \begin{itemize}

%MRS9: sorry, I keep reading ``no correlation'' as ``no collusion'' :)
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_nocorrelation.png}
  \caption{}\label{fig:sf_qy_nocorrelation}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qy_correlation.png}
  \caption{}\label{fig:sf_qy_correlation.png}
  \end{subfigure} 
  \begin{subfigure}{0.3\textwidth}
  \includegraphics[width=\textwidth]{sf_qz_correlation.png}
  \caption{}\label{fig:sf_qz_correlation.png}
  \end{subfigure}   
  \caption{We generated X-ray diffraction patterns for simplified systems consisting of 
  points meant to represent monomer head groups. We added a similar amount of noise to 
  that seen in our simulations. (a) We added Gaussian noise to each particle in the $z$, 
  $\theta$ and $r$ directions. The $q_y$ cross-section of R-$\pi$ contains three sharp
  peaks. (b) When we make points in each column correlated, the intensity of R-$\pi$ 
  increases but the sharp peaks remain with the same ratio of intensity between the
  center and outer peaks. (c) 
  %MRS9: I'm not sure what you mean by ``correlation'' broadening peaks here.  Do you mean replacing exact periodicity by 
  %correlated random points  Because that reduces correlation (from 100% to less than 100%).
Correlation between scatterers in the $z$-direction causes
  R-$\pi$ to broaden in the $q_z$ direction.}\label{fig:sf_correlation}
  %MRS9: in c, weird that the orange peaks are broader, but taller. Not sure I understand. 
  \end{figure}

  Scatterers in each column are correlated with each other. In the simplified 
  system described above, we added uncorrelated Gaussian noise in the 
  z-direction which ignores any interaction head groups might have with each
  other. To remedy this, we randomly sampled a multivariate normal distribution
  with the same 
  %variance, v, 
  standard deviation, $\sigma$.
  implied by Table~\ref{table:quenched_disorder}. We 
  defined the distribution using a covariance matrix such that the covariance
  in position, z, between scatterers decays exponentially from v according to the
  equation $ve^{-z/L}$, where L is the correlation length. Experimentally, the
  correlation length can be estimated as the inverse of the FWHM of the $q_z$
  cross-section of R-$\pi$.  %BJC8: needs references 
  Accordingly, the correlation length of the experimental system is $\geq$ 9 
  $\AA$. The value may be larger since the peak is likely broadened for a variety
  of other reasons. %BJC8: the reasons I can provide more detail on above.  
  %BJC8: Can show correlation effect on intensity in supporting info

@@

  %BJC8: The next couple paragraphs is all old stuff that can likely be cut down a bit. But I think 
  % this is where I'd put this discussion.
  Monomers in the ordered basin stack closer together than those in the disordered basin
  (Table~\ref{table:correlation_length}). We calculated the equilibrated vertical distance,
  $\mathit{d}_{equil}$, between monomers using Equation~\ref{eqn:decaying_sinusoid}. 
  Monomers in the ordered basin stack ca. 0.2 and 0.3 \AA~closer than those built in the 
  disordered basin in the sandwiched and parallel displaced configurations respectively. 
  The distance between stacked monomers is greater than experiment by 0.5--0.9 \AA~across all 
  cases,
  %MRS9: added
  with disordered basins at the high part of that range 0.2 and 0.3 \AA~more distant.
  %MRS9: GAFF could OVER predict pi-pi stacking, best to include citations here that it does indeed overpredict.
This behavior is not surprising since GAFF models atoms as point charges and does not 
  appropriately model the aromatic $\pi-\pi$ interactions which would make it more energetically
  favorable for the monomers to stack closer together. 
Additionally, it is possible that the 
  tails prevent close stacking of monomer head groups and we do not achieve the timescales 
  necessary for them to rearrange into a necessarily more tightly packed configuration. Ordered
  basin systems are likely the best choice for transport studies. 
%MRS9: make it clearer if the last sentence is a conclusion based on the other evidence in the paragraph.

@@

  When we allow monomer columns to move independently in the z-direction, the intensity
  of R-$\pi$ drops and the $q_r$ cross-section of the simulated diffraction patterns 
  smooths out.
  \begin{itemize}
  	\item Allowing columns to move independently smooths out the $q_r$ cross-section. Any amount
  	of dependence results in sharp peaks.
  	\item R-$\pi$ intensity decreases by up to 10x
  	\item Can put R-$\pi$ intensity vs. column independence in supporting info.
  	\item Predict level of independence in simulation (what amount of displacement cause the 
  	R-$\pi$ profile to look like that shown in Figure 8d). %MRS9: this is a bit complicated, since it could be a combination of factors.
  	\item Figure: (a) x \% column displacement give Figure 8d (b) Independent columns give a smooth
  	curve %MRS9: not quite sure what you are talking about in this figure.  Could you give more information?
  \end{itemize}

  Increasing thermal noise in the x and y directions causes R-$\pi$ to sharpen in the 
  $q_r$ direction. %MRS9: this is unanticiated (noise creating sharpening) so will have to make it clear.
  \begin{itemize}
    \item $q_r$ cross-section still too broad
    \item Adding more thermal noise sharpens it
    \item Figure: Overlay thinner FWHM plot on top of wider FWHM 
  \end{itemize}

%MRS9: the statement below is pretty strong, need to back it up.  We know that we have quenched noise, which is a type of over-ordering - is that taken into account?  
  We have nearly the right amount of disorder / noise in our system, but correlation 
  between columns really messes up R-$\pi$.

@@

  The system size 
  %MRS9: added
  in the $z$-direction.
  does not significantly alter the intensity of R-$\pi$. We equilibrated a 
  sandwiched system with twice as many monomers per column so that the system size doubled in 
  the z-direction. The correlation length increases modestly from 4.5 $\pm$ 0.4 to 7.3 $\pm$ 1.2 \AA, 
  and the intensity of R-$\pi$ decreases from 44.0 to 39.4. Visually, the correlation functions
  are nearly identical (See Figure~S-\ref{S-fig:z_correlation_overlay}).
